\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-17 doc/flexiblesusy-paper.tex
Changed description of the two loop Higgs corrections in section 6.5 to match new plan which we agreed upon and Alex has implemented.

\item \code{HighPoleMassPrecision}: This option solves
  Eq.~\eqref{eq:pole-mass-def} exactly by iterating over the momentum
  $p$.  It therefore provides the determination of the pole masses
  with highest precision, but has also the highest execution time.
  Here the one-loop mass matrix $m_{f,1L}^\text{high}$ is diagonalized
  $n$ times, as in the case of \code{MediumPoleMassPrecision},
  resulting in $n$ pole masses $m_{f_k}^\pole$ ($k = 1,\ldots,n$).
  Afterwards, the diagonalization is repeated, this time using the
  calculated pole masses $m_{f_k}^\pole$ for the momentum calculation
  $p^2 = (m_{f_k}^\pole)^2$.  The iteration stops if convergence is
  reached.
\end{itemize}
%
If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  The former enables two-loop Higgs FORTRAN routines
supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
which add two-loop corrections of $\oatas$, $\oabas$, $\oatq$,
$\oabq$, $\oatauq$ and $\oatab$.  The latter adds corrections
calculated in the NMSSM at $\oatas$, $\oabas$ from
\cite{Degrassi:2009yq}. If wants to include the $\oatq$, $\oabq$,
$\oatauq$ and $\oatab$ the MSSM pieces are used though it NMSSM
corrections at $\oatas$, $\oabas$ along with the MSSM corrections at
$\oatq$, $\oabq$, $\oatauq$ and $\oatab$ then both flags
\code{UseHiggs2LoopMSSM} and \code{UseHiggs2LoopNMSSM} should be set
to \code{True}.  Since the Higgs mass is a very important measurement
and the two-loop corrections can be larger than the current
experimental error \cite{Degrassi:2009yq} we recommend to set these
switches to \code{True} in any MSSM-\footnote{In \fs a model is
  MSSM-like if (i) its superpotential is approximately given by the
  MSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains two CP-even and CP-odd Higgs bosons,
  where one CP-odd Higgs boson may be a Goldstone boson, all with an
  MSSM-like coupling to $t$, $b$ and $\tau$.} and
NMSSM-like\footnote{In \fs a model is NMSSM-like if (i) its
  superpotential is approximately given by the NMSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains three CP-even and CP-odd Higgs bosons, where one or
  two CP-odd Higgs bosons may be Goldstone bosons, all with an
  NMSSM-like coupling to $t$, $b$ and $\tau$\@.  Examples for
  NMSSM-like models are the USSM and the \ESSM.} model.  However in
such models the user should still consider whether these corrections
are really the leading corrections in the model or if there are other
potentially large two-loop corrections.  For models
with a more extended Higgs sector we recommend that the leading log
two-loop corrections are estimated by generalizing those of the MSSM
or NMSSM.

>>>>

\item \code{HighPoleMassPrecision}: This option solves
  Eq.~\eqref{eq:pole-mass-def} exactly by iterating over the momentum
  $p$.  It therefore provides the determination of the pole masses
  with highest precision, but has also the highest execution time.
  Here the one-loop mass matrix $m_{f,1L}^\text{high}$ is diagonalized
  $n$ times, as in the case of \code{MediumPoleMassPrecision},
  resulting in $n$ pole masses $m_{f_k}^\pole$ ($k = 1,\ldots,n$).
  Afterwards, the diagonalization is repeated, this time using the
  calculated pole masses $m_{f_k}^\pole$ for the momentum calculation
  $p^2 = (m_{f_k}^\pole)^2$.  The iteration stops if convergence is
  reached.
\end{itemize}
%
If higher accuracy is required, two-loop corrections to the
self-energies can be added by setting \code{UseHiggs2LoopMSSM = True}
in the MSSM or \code{UseHiggs2LoopNMSSM = True} in the NMSSM in the
model file.  The former provides routines that call the two-loop Higgs
FORTRAN routines supplied by P.~Slavich from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}
for calculating corrections of $\oatas$, $\oabas$, $\oatq$, $\oabq$,
$\oatauq$ and $\oatab$.  The latter adds corrections calculated in the
NMSSM at $\oatas$, $\oabas$ from \cite{Degrassi:2009yq} and partial
corrections for the order $\oatq$, $\oabq$, $\oatauq$ and $\oatab$ from the
MSSM.  These corrections can then be included in the
calculation of the Higgs pole masses when running the spectrum
generator by setting the appropriate SLHA flags.

{\color{red} To include all two loop corrections which have been
  generated the user may simply set entry 4 of the FlexibleSUSY block
  in the SLHA file to 2.  The user may also want to include only some of
  the corrections generated, for example in the NMSSM the user may decide not to use the partial corrections at order $\oatq$, $\oabq$, $\oatauq$ and $\oatab$ which have been computed in the MSSM. In that case the entries 9,10,11 and 12 may be used to switch on and off corrections at specific orders, 1 meaning the correction is included and 2 means the correction is not.  Alex: can you check this part matches what you did and maybe fox details a little and also we should decide if it belongs here or if describe SLHA stuff later.}

Since the Higgs mass is a very important measurement and
the two-loop corrections can be larger than the current experimental
error \cite{Degrassi:2009yq} we recommend to set these switches to
\code{True} in any MSSM-\footnote{In \fs a model is MSSM-like if (i)
  its superpotential is approximately given by the MSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains two CP-even and CP-odd Higgs bosons, where one CP-odd
  Higgs boson may be a Goldstone boson, all with an MSSM-like coupling
  to $t$, $b$ and $\tau$.} and NMSSM-like\footnote{In \fs a model is
  NMSSM-like if (i) its superpotential is approximately given by the
  NMSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains three CP-even and CP-odd Higgs
  bosons, where one or two CP-odd Higgs bosons may be Goldstone
  bosons, all with an NMSSM-like coupling to $t$, $b$ and $\tau$\@.
  Examples for NMSSM-like models are the USSM and the \ESSM.} model.
However in such models the user should still consider whether these
corrections are really the leading corrections in the model or if
there are other potentially large two-loop corrections.  For models
with a more extended Higgs sector we recommend that the leading log
two-loop corrections are estimated by generalizing those of the MSSM
or NMSSM.
